---
title: "T20 batsmen and bowler template"
author: "Tinniam V Ganesh"
date: "February 25, 2017"
output: html_document
---

###1 Batsman functions
Get the batsman's details for a batsman

```{r}
setwd("../BattingBowlingDetails")
kohli <- getBatsmanDetails(team="India",name="Kohli",dir=".")
batsmanDF <- getBatsmanDetails(team="country1",name="batsmanName",dir=".")
```

###2. Runs vs deliveries
```{r}
batsmanRunsVsDeliveries(batsmanDF,"batsmanName")
```

###3. Batsman 4s & 6s
```{r}
batsman46 <- select(batsmanDF,batsman,ballsPlayed,fours,sixes,runs)
p1 <- batsmanFoursSixes(batsman46,"batsmanName")
```

###4. Batsman dismissals
```{r}
batsmanDismissals(batsmanDF,"batsmanName")
```

###5. Runs vs Strike rate
```{r}
batsmanRunsVsStrikeRate(batsmanDF,"batsmanName")
```

###6. Batsman Moving Average
```{r}
batsmanMovingAverage(batsmanDF,"batsmanName")
```


###7. Batsman cumulative average
```{r}
batsmanCumulativeAverageRuns(batsmanDF,"batsmanName")
```

###8. Batsman cumulative strike rate
```{r}
batsmanCumulativeStrikeRate(batsmanDF,"batsmanName")
```

###9. Batsman runs against oppositions
```{r}
batsmanRunsAgainstOpposition(batsmanDF,"batsmanName")
```

###10. Batsman runs vs venue
```{r}
batsmanRunsVenue(batsmanDF,"batsmanName")
```

###11. Batsman runs predict
```{r}
batsmanRunsPredict(batsmanDF,"batsmanName")
```

###12. Bowler functions
For example to get Ravicahnder Ashwin's bowling details
```{r}
setwd("../BattingBowlingDetails")
ashwin <- getBowlerWicketDetails(team="India",name="Ashwin",dir=".")
bowlerDF <- getBatsmanDetails(team="country1",name="bowlerName",dir=".")
```

###13. Bowler Mean Economy rate
```{r}
bowlerMeanEconomyRate(bowlerDF,"bowlerName")
```

###14. Bowler mean runs conceded
```{r}
bowlerMeanRunsConceded(bowlerDF,"bowlerName")
```

###15. Bowler Moving Average
```{r}
bowlerMovingAverage(bowlerDF,"bowlerName")
```

###16. Bowler cumulative average wickets
```{r}
bowlerCumulativeAvgWickets(bowlerDF,"bowlerName")
```

###17. Bowler cumulative Economy Rate (ER)
```{r}
bowlerCumulativeAvgEconRate(bowlerDF,"bowlerName")
```

###18. Bowler wicket plot
```{r}
bowlerWicketPlot(bowlerDF,"bowlerName")
```

###19. Bowler wicket against opposition
```{r}
bowlerWicketsAgainstOpposition(bowlerDF,"bowlerName")
```


###20. Bowler wicket at cricket grounds
```{r}
bowlerWicketsVenue(bowlerDF,"bowlerName")
```

###21. Predict number of deliveries to wickets
```{r}
setwd("./T20Matches")
bowlerDF1 <- getDeliveryWickets(team="country1",dir=".",name="bowlerName",save=FALSE)
bowlerWktsPredict(bowlerDF1,"bowlerName")
```
