---
title: "T20 Match Template"
author: "Tinniam V Ganesh"
date: "February 25, 2017"
output: html_document
---


###1 International T20 Match Analysis
Load any match data from the ./T20Matches folder for e.g. Afganistan-England-2016-03-23.RData

```{r}
setwd("./T20Matches")
load("Afghanistan-England-2016-03-23.RData")
afg_eng<- overs
#The steps are
load("Country1-Country2-Date.Rdata")
country1_country2 <- overs
```


All analysis for this match can be done now
###2. Scorecard
```{r}
teamBattingScorecardMatch(country1_country2,"Country1")
teamBattingScorecardMatch(country1_country2,"Country2")
```

###3.Batting Partnerships
```{r}
teamBatsmenPartnershipMatch(country1_country2,"Country1","Country2")
teamBatsmenPartnershipMatch(country1_country2,"Country2","Country1")
```

###4. Batsmen vs Bowler Plot
```{r}
teamBatsmenVsBowlersMatch(country1_country2,"Country1","Country2",plot=TRUE)
teamBatsmenVsBowlersMatch(country1_country2,"Country1","Country2",plot=FALSE)
```

###5. Team bowling scorecard
```{r}
teamBowlingScorecardMatch(country1_country2,"Country1")
teamBowlingScorecardMatch(country1_country2,"Country2")
```

###6. Team bowling Wicket kind match
```{r}
teamBowlingWicketKindMatch(country1_country2,"Country1","Country2")
m <-teamBowlingWicketKindMatch(country1_country2,"Country1","Country2",plot=FALSE)
m
```
###7. Team Bowling Wicket Runs Match
```{r}
teamBowlingWicketRunsMatch(country1_country2,"Country1","Country2")
m <-teamBowlingWicketRunsMatch(country1_country2,"Country1","Country2",plot=FALSE)
m
```

###8. Team Bowling Wicket Match
```{r}
m <-teamBowlingWicketMatch(country1_country2,"Country1","Country2",plot=FALSE)
m
teamBowlingWicketMatch(country1_country2,"Country1","Country2")
```
###9. Team Bowler vs Batsmen
```{r}
teamBowlersVsBatsmenMatch(country1_country2,"Country1","Country2")
m <- teamBowlersVsBatsmenMatch(country1_country2,"Country1","Country2",plot=FALSE)
m
```
###10. Match Worm chart
```{r}
matchWormGraph(country1_country2,"Country1","Country2")
```

