---
title: "T20 Template with yorkr"
author: "Tinniam V Ganesh"
date: "February 25, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

In this post I create yorkr templates for International T20 matches that
are avialble on Cricsheet. While I have already done this with my latest post
Inswinger  in which I downladed data from Dec 2016, I cant keep 
so I cam creating this detailed post with all the steps needed
for T20 analysis anytime as more matches ate played around the WorldPhones
and more data is added to Cricsheet

```{r}
library(yorkr)
library(dplyr)
```
# The first few steps take care of te al;l the data setup. This needs
to be done before any of the analysis of T10 batsmen, bowlers, T20 match,
matches between any 2 T20 countries or analysis of a teams performance against all
other countries

There will be 5 folders at the root

1. T20data
2. T20Matches
3. T20MatchesBetween2Teams
4. allMatchesAllOpposition
5. BattingBowlingDetails


# The source YAML files will be in T20Data folder
# 1.Create directory T20Matches
Some file conversions may give a problem. You could try to debug the
problem or just remove it from the T20Data. At most  2 -4 file will have 
conversion problems and I ignore these.

```{r }
convertAllYaml2RDataframesT20("T20Data","T20Matches")
```

### 2.Save all matches between all combinations of T20 nations
This function will create the set of all matches between every T20 country
against every other T20 country. This uses the data that was created in T20Matches,
with the convertAllYaml2RDataframesT20() function.
```{r}
setwd("./T20MatchesBetween2Teams")
saveAllMatchesBetweenTeams("../T20Matches")
```

### 3.Save all matches against all opposition
This will create a consolidated dataframe of all matches played by every T20 playing
nation against all other nattions. This also uses the data that was created in T20Matches,
with the convertAllYaml2RDataframesT20() function.
```{r}
setwd("../allMatchesAllOpposition")
saveAllMatchesAllOpposition("../T20Matches")
```

###4. Create batting and bowling details for each T20 country
These are the current T20 playing nations. You can add to this vector
as more countries start playing T20. You will get to know all T20 nations
by also look at the directory created above namely allMatchesAllOpposition.
his also uses the data that was created in T20Matches,
with the convertAllYaml2RDataframesT20() function.
```{r}
setwd("../BattingBowlingDetails")
teams <-c("Australia","India","Pakistan","West Indies", 'Sri Lanka',
          "England", "Bangladesh","Netherlands","Scotland", "Afghanistan",
          "Zimbabwe","Ireland","New Zealand","South Africa","Canada",
          "Bermuda","Kenya","Hong Kong","Nepal","Oman","Papua New Guinea",
          "United Arab Emirates")

for(i in seq_along(teams)){
    print(teams[i])
    val <- paste(teams[i],"-details",sep="")
    val <- getTeamBattingDetails(teams[i],dir="../T20Matches", save=TRUE)

}

for(i in seq_along(teams)){
    print(teams[i])
    val <- paste(teams[i],"-details",sep="")
    val <- getTeamBowlingDetails(teams[i],dir="../T20Matches", save=TRUE)

}
```

###5. Get the list of batsmen for a particular country
For e.g. if you wanted to get the batsmen of Canada you would do the following. By
replacing Canada for any other country you can get the batsmen of that country.
These batsmen names can then be used in the batsmen analysis

```{r}
country="Canada"
teamData <- paste(country,"-BattingDetails.RData",sep="")
load(teamData)
countryDF <- battingDetails
bmen <- countryDF %>% distinct(batsman) 
bmen <- as.character(bmen$batsman)
batsmen <- sort(bmen)
batsmen
```

###6. Get the list of bowlers for a particular country
The method below can get the list of bowler names for any T20 nation. These
names can then be used in the bowler analysis below
```{r}
country="Netherlands"
teamData <- paste(country,"-BowlingDetails.RData",sep="")
load(teamData)
countryDF <- bowlingDetails
bwlr <- countryDF %>% distinct(bowler) 
bwlr <- as.character(bwlr$bowler)
bowler <- sort(bwlr)
bowler
```

### Now we are all set

