---
title: "T20 Template with yorkr"
author: "Tinniam V Ganesh"
date: "February 25, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

In this post I create yorkr templates for International T20 matches that
are available on [Cricsheet](http://cricsheet.org/ ). With these templates you can convert all
T20 data which is in yaml format to R dataframes. Further I create data and the necessary 
templates for analyzing. All of these can be accessed at [yorkrT20Template](https://github.com/tvganesh/yorkrT20Template). The templates are


1. Template for conversion and setup - T20Template.Rmd
1. Any T20 match - T20Matchtemplate.Rmd
2. T20 matches between 2 nations - T20Matches2TeamTemplate.Rmd
3. A T20 nations performance against all other T20 nations - T20AllMatchesAllOppnTemplate.Rmd
4. Analysis of T20 batsmen and bowlers of all T20 nations - T20BatsmanBowlerTemplate.Rmd

Besides the templates the repository also includes the converted data for all T20 
matches I downloaded  from Cricsheet in Dec 2016, You can recreate the files as
more matches are added to Cricsheet site. This post contains all the steps needed
for T20 analysis,  as more matches are played around the World and more 
data is added to Cricsheet. This will also be my reference in future if I decide to
analyze T20 in future!

There will be 5 folders at the root

1. T20data - Match files as yaml from Cricsheet
2. T20Matches - Yaml match files converted to dataframes
3. T20MatchesBetween2Teams - All Matches between any 2 T20 teams
4. allMatchesAllOpposition - A T20 countries match data against all other teams
5. BattingBowlingDetails - Batting and bowling details of all countries

```{r}
library(yorkr)
library(dplyr)
```
The first few steps take care of the  data setup. This needs
to be done before any of the analysis of T20 batsmen, bowlers, any T20 match,
matches between any 2 T20 countries or analysis of a teams performance against all
other countries

There will be 5 folders at the root

1. T20data
2. T20Matches
3. T20MatchesBetween2Teams
4. allMatchesAllOpposition
5. BattingBowlingDetails


# The source YAML files will be in T20Data folder
# 1.Create directory T20Matches
Some files may give  conversions errors. You could try to debug the
problem or just remove it from the T20data folder. At most  2-4 file will have 
conversion problems and I usally remove then from the files to be 
converted. 

Also take a look at my [Inswinger](https://tvganesh.shinyapps.io/inswingerFinal/) shiny
app which was created after performing the same conversion on the Dec 16 data
.

```{r }
convertAllYaml2RDataframesT20("T20Data","T20Matches")
```

### 2.Save all matches between all combinations of T20 nations
This function will create the set of all matches between every T20 country
against every other T20 country. This uses the data that was created in T20Matches,
with the convertAllYaml2RDataframesT20() function.
```{r}
setwd("./T20MatchesBetween2Teams")
saveAllMatchesBetweenTeams("../T20Matches")
```

### 3.Save all matches against all opposition
This will create a consolidated dataframe of all matches played by every T20 playing
nation against all other nattions. This also uses the data that was created in T20Matches,
with the convertAllYaml2RDataframesT20() function.
```{r}
setwd("../allMatchesAllOpposition")
saveAllMatchesAllOpposition("../T20Matches")
```

###4. Create batting and bowling details for each T20 country
These are the current T20 playing nations. You can add to this vector
as more countries start playing T20. You will get to know all T20 nations
by also look at the directory created above namely allMatchesAllOpposition.
his also uses the data that was created in T20Matches,
with the convertAllYaml2RDataframesT20() function.
```{r}
setwd("../BattingBowlingDetails")
teams <-c("Australia","India","Pakistan","West Indies", 'Sri Lanka',
          "England", "Bangladesh","Netherlands","Scotland", "Afghanistan",
          "Zimbabwe","Ireland","New Zealand","South Africa","Canada",
          "Bermuda","Kenya","Hong Kong","Nepal","Oman","Papua New Guinea",
          "United Arab Emirates")

for(i in seq_along(teams)){
    print(teams[i])
    val <- paste(teams[i],"-details",sep="")
    val <- getTeamBattingDetails(teams[i],dir="../T20Matches", save=TRUE)

}

for(i in seq_along(teams)){
    print(teams[i])
    val <- paste(teams[i],"-details",sep="")
    val <- getTeamBowlingDetails(teams[i],dir="../T20Matches", save=TRUE)

}
```

###5. Get the list of batsmen for a particular country
For e.g. if you wanted to get the batsmen of Canada you would do the following. By
replacing Canada for any other country you can get the batsmen of that country.
These batsmen names can then be used in the batsmen analysis

```{r}
country="Canada"
teamData <- paste(country,"-BattingDetails.RData",sep="")
load(teamData)
countryDF <- battingDetails
bmen <- countryDF %>% distinct(batsman) 
bmen <- as.character(bmen$batsman)
batsmen <- sort(bmen)
batsmen
```

###6. Get the list of bowlers for a particular country
The method below can get the list of bowler names for any T20 nation. These
names can then be used in the bowler analysis below
```{r}
country="Netherlands"
teamData <- paste(country,"-BowlingDetails.RData",sep="")
load(teamData)
countryDF <- bowlingDetails
bwlr <- countryDF %>% distinct(bowler) 
bwlr <- as.character(bwlr$bowler)
bowler <- sort(bwlr)
bowler
```

### Now we are all set

